Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-21 docs/report/report.tex
Update PID section of report

\subsection{Controller and State Monitoring}
In this project we assumethat the quadrotor has successfully rendezvoused with the target vehicle and at all time has a clear view through the camera image of the landing target located on the target vehicle. The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle. Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must begin to descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved. Ideally the quadrotor will descend more rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just before it hits the target in order to minimize time and energy requirements of the landing Vancouver.

In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands to reduce the horizontal and vertical distance between the quadrotor and the landing platform. During the approach the PIDz controller attempts to maintain a safe approach altitude such that the target does not go out of view during stage one. Once a these hold displacement value in x and y is achieve the $PID_z$ controller is set a set of commands that smoothly move the quadrotor to a landing position.

The PIDx and PIDy are designed such that thier output is mapped to attitude commands in the pitch and roll relative to the quadrotor frame as outlined in Equations \ref{PIDx}, \ref{PIDy}, \ref{PIDz} . The commanded throttle is also adjusted to account for the commanded roll and pitch using Equation \ref{Adjusted Throttle} to better maintain altitude when $\phi_t$ and $\psi_t$ are non-zero.

\begin{equation}
	\label{PIDx}
	\hat{\psi_t} = cos(\theta) \left(K_p e_x + K_i \sum_{t = 0}^{t} e_{x, t} dt + K_d \dot{e}_{x,t} \right)
\end{equation}q

\begin{equation}
	\label{PIDy}
	\phi_t = sin(\theta) \left( K_p e_y + K_i \sum_{t=0}^{t} \dot{e_y}_{,t} dt + K_d \dot{e_y}_{,t} \right)
\end{equation}

\begin{equation}
	\label{PIDz}
	Thrust_z = K_p e_z + K_i \sum_{t=0}^{t} \dot{e_z}_{,t} dt + K_d \dot{e_z}_{,t} 
\end{equation}

\begin{equation}
	\label{Adjusted Throttle}
	AdjustedThrust = \frac{Thrust_z}{cos(\phi_t) cos(\psi_t)}
\end{equation}

>>>>

\subsection{Controller and State Monitoring}
In this project we assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all times. The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle. Next, while maintaining the near zero displacements in the x and y directions, the quadrotor descends at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved. Ideally the quadrotor will descend rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just abvove ($\approx 1m$) the landing target inorder to minimize time and energy requirements of the landing maneouver.

In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as a altitude command to maintain a safe approach altitude such that the target does not go out of view during landing. We omit yaw control as we assume the quadrotor will be axis aligned with the direction of travel of the moving target.

The position controller takes the quadrotor's desired position and current position in $x$, $y$ and $z$ of the world frame as inputs, these inputs are mapped to attitude and altitude commands in the roll, pitch and thrust relative to the quadrotor frame as outlined in Equations \ref{eq:pid_roll}, \ref{eq:pid_pitch}, \ref{eq:pid_thrust}. The outputs of Equations \ref{eq:pid_roll}, \ref{eq:pid_pitch} are then adjusted to account for the yaw $\theta$ changes as in Equation \ref{eq:pid_roll_adjusted} and \ref{eq:pid_pitch_adjusted}, the altitude commanded is adjusted when roll $\phi$ and pitch $\theta$ are non-zero to maintain altitude.

\begin{equation}
	\label{eq:pid_roll}
	\hat{\phi_t} = K_p e_x + K_i \sum_{t = 0}^{t} e_{x, t} dt + K_d \dot{e}_{x,t}
\end{equation}

\begin{equation}
	\label{eq:pid_pitch}
	\hat{\theta_t} = K_p e_y + K_i \sum_{t = 0}^{t} \dot{e}_{y,t} dt + K_d \dot{e}_{y ,t}
\end{equation}

\begin{equation}
	\label{eq:pid_thrust}
	\hat{T_z} =
		K_p e_z + K_i \sum_{t=0}^{t} \dot{e_z}_{,t} dt + K_d \dot{e_z}_{,t} 
\end{equation}

\begin{equation}
	\label{eq:pid_roll_adjusted}
	\phi_t = \cos(\psi_t) \hat{\phi_t} - \sin(\psi_t) \hat{\theta_t}
\end{equation}

\begin{equation}
	\label{eq:pid_pitch_adjusted}
	\theta_t = \sin(\psi_t) \hat{\phi_t} + \cos(\psi_t) \hat{\theta_t}
\end{equation}

\begin{equation}
	\label{Adjusted Throttle}
	T = 
		T_{\text{hover}} +
		\frac{\hat{T_{z}}}{cos(\phi_t) cos(\theta_t)}
\end{equation}
